Binocular integration of chromatic and luminance signals

### 2024-04-01 manuscript.qmd
Trying again
Testing specified latex engine, and also reticulate function

---
title: "Binocular integration of chromatic and luminance signals"
author:
  - Daniel H. Baker
  - Kirralise J. Hansford
  - Federico G. Segala
  - Annie Y. Morsi
  - Rowan J. Huxley
  - Joel T. Martin
  - Maya Rockman
  - Alex R. Wade
format: pdf
execute:
  echo: false
bibliography: references.bib
csl: journal-of-vision.csl
header-includes: 
  \usepackage{float} \floatplacement{figure}{H} 
  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{A\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{A\arabic{figure}}}
---

@@

if (processdata>0){
  install_miniconda()
  use_miniconda('r-reticulate')
  py_install('https://github.com/wichmann-lab/python-psignifit/zipball/master')
  # install psignifit in the terminal with:
  # sudo pip install https://github.com/wichmann-lab/python-psignifit/zipball/master
  ps <- import('psignifit')
  # calculate constant to scale the slope parameter to the Gaussian SD
  C <- ps$utils$my_norminv(1-0.05,0,1) - ps$utils$my_norminv(0.05,0,1)
}

>>>>

---
title: "Binocular integration of chromatic and luminance signals"
author:
  - Daniel H. Baker
  - Kirralise J. Hansford
  - Federico G. Segala
  - Annie Y. Morsi
  - Rowan J. Huxley
  - Joel T. Martin
  - Maya Rockman
  - Alex R. Wade
format:
  pdf:
    keep-tex: true
pdf-engine: xelatex
execute:
  echo: false
bibliography: references.bib
csl: journal-of-vision.csl
header-includes: 
  \usepackage{float} \floatplacement{figure}{H} 
  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{A\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{A\arabic{figure}}}
---

@@

if (processdata>0){
  # install_miniconda()
  # use_miniconda('r-reticulate')
  # py_install('https://github.com/wichmann-lab/python-psignifit/zipball/master')
  # install psignifit in the terminal with:
  # sudo pip install https://github.com/wichmann-lab/python-psignifit/zipball/master
  ps <- import('psignifit')
  # calculate constant to scale the slope parameter to the Gaussian SD
  C <- ps$utils$my_norminv(1-0.05,0,1) - ps$utils$my_norminv(0.05,0,1)
}
